The necessity of hypermedia RDF and an approach to achieve it

### 2012-03-22 eswc-2012/workshop2.tex
note read-write scenario in conclusion
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@167 43ef1190-90fd-4dd7-a769-d0121f02b80e
Ooops
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@192 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{abstract}
This paper will give an overview of the practical implications of the
HATEOAS constraint of the REST architectural style, and in that light argue why
hypermedia RDF is a practical necessity. We will then sketch a
vocabulary for hypermedia RDF using Mike Amundsen's H~Factor
classification as motivator. Finally, we will briefly argue that
SPARQL is important when making non-trivial traversals of Linked Data
graphs, and see how to a bridge between Linked Data and SPARQL may be
created with hypermedia RDF.
\end{abstract}

@@

We have shown how RDF serializations can become very powerful
hypermedia types by using a simple vocabulary. We have argued briefly
that some triples should be added to every information resource, but
note that most triples are only relevant to write-operations and
should only appear in that case. We also noted that SPARQL is
important for non-trivial traversal of Linked Data. To sum up, the
addition of the following triples would make life easier for
developers of applications that use Semantic Web data:

>>>>

\begin{abstract}
This paper will give an overview of the practical implications of the
HATEOAS constraint of the REST architectural style, and in that light argue why
hypermedia RDF is a practical necessity. We will then sketch a
vocabulary for hypermedia RDF using Mike Amundsen's H~Factor
classification as motivator. Finally, we will briefly argue that
SPARQL is important when making non-trivial traversals of Linked Data
graphs, and see how a bridge between Linked Data and SPARQL may be
created with hypermedia RDF.
\end{abstract}

@@

We have shown how RDF serializations can become very powerful
hypermedia types by using a simple vocabulary. As a consequence,
developers can use Linked Data in a read-write scenario without
specialized knowledge about RDF APIs or other out-of-band
information. We have argued briefly that some triples should be added
to every information resource, but note that most triples are only
relevant to write-operations and should only appear in that case. We
also noted that SPARQL is important for non-trivial traversal of
Linked Data. To sum up, the addition of the following triples would
make life easier for developers of applications that use Semantic Web
data:
